Post-replication citation patterns in psychology: Four case studies

### 2021-04-27 manuscript/appendix.Rmd
added raw citation curves to appendix

# Tabular data for citation curves, citation valence, and co-citation of replications {#appC}

@@

>>>>

# Non-standardized data for citation curves, citation valence, and co-citation of replications {#appC}

@@

```{r citeCurvesRaw, fig.cap='Annual citation counts (non-standardized; solid line) for the five original studies. The black arrow indicates the year in which the replication was published.', fig.width=12, fig.height=12.5, fig.path='figs/', dev=c('png', 'pdf')}
ggarrange(
  ggarrange(citationCurve("strack", thisTitle = "Strack et al. (1988)", standardized = F, plotReference = F, areaPlot = F),
    citationCurve("baumeister", thisTitle = "Baumeister et al. (1998)", standardized = F, plotReference = F, areaPlot = F),
    nrow = 2, ncol = 1, common.legend = T
  ),
  ggarrange(citationCurve("sripada", thisTitle = "Sripada et al. (2014)", standardized = F, plotReference = F, areaPlot = F),
    citationCurve("carter", thisTitle = "Carter et al. (2011)", standardized = F, plotReference = F, areaPlot = F),
    citationCurve("caruso", thisTitle = "Caruso et al. (2013)", standardized = F, plotReference = F, areaPlot = F),
    nrow = 1, ncol = 3, common.legend = F
  ),
  nrow = 2, ncol = 1, heights = c(2, 1)
) %>%
  annotate_figure(
    left = text_grob("Citation count (non-standardized)", rot = 90, size = 20),
    bottom = text_grob("Publication year", size = 20)
  )
```
